Appendix

### 2020-06-22 manuscript/article.tex
version 0.1

\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Getulio Vargas Foundation, Brazil, \url{huzeyfealptekin@gmail.com}.} \hspace{.5cm} Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \url{danilofreire@gmail.com}, \url{http://danilofreire.github.io}. Corresponding author.} \hspace{.5cm} Umberto Mignozzetti\thanks{Assistant Professor, Department of International Relations, Getulio Vargas Foundation, Brazil, \url{umberto.mignozzetti@fgv.br}, \url{http://umbertomig.com}.} \hspace{.5cm} Catarina Roman\thanks{Research Associate, Department of International Relations, Getulio Vargas Foundation, Brazil, \url{catarinamroman@gmail.com}.}}

@@

\vspace{.4cm}
\noindent \textbf{Keywords:} distributive politics; government budget; law of
$1/n$; legislature size; meta-analysis; public spending

@@

\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Level & \raggedleft Electoral System

@@

R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & Municipal & M\\
R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & Municipal & M\\
T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & State & NM\\
\begin{tabular}[t]{@{}l@{}}T. Bjedov,\\ S. Lapointe \& \\T. Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Canton & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}J. Drew \& \\ B. Dollery\end{tabular} & The Price of Democracy? Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & State & NM\\
\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}N. Fiorino \& \\ R. Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & Region & NM\\
\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & Municipal & NM\\
\begin{tabular}[t]{@{}l@{}}A. Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Municipal & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & District & M\\
\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & District & NM\\
\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & State & NM\\
\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & Municipal & M\\
\begin{tabular}[t]{@{}l@{}}B. Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}B. Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}P. Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government? Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & Municipal & NM\\
\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}C. Schaltegger \& \\ L. Feld\end{tabular} & Do Large Cabinets Favor Large Governments? Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Canton & NM\\
\begin{tabular}[t]{@{}l@{}}E. Stein,\\ E. Talvi \& \\ A. Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub. & 1998 & Multiple (26) & Country & NM\\ [1ex]

@@

M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
Country codes follow the ISO 3166-1 alpha-3 international standard.}

@@

We also coded four moderators that frequently appear in the literature and may
help us understand the heterogeneity in the reported results. We included them
in our meta-regressions alongside an indicator for the type of independent
variable used in the original study ($n$, log($n$), or $k$). The additional
moderators are: 1) publication year; 2) paper publication in an academic
journal; 3) electoral system; 4) estimation method. Publication years have a
mean of 2009.6, and a standard deviation of 6.5. Twenty-two papers had been
published and 4 remained unpublished when we finished the data collection. In
our sample, 13 articles focus on majoritarian systems and 15 on mixed or
proportional representation systems.\footnote{Note that this moderator is
important for our estimations both theoretically and empirically. This because
\citet{weingast1981political} formulated their theory under the assumption that
the electoral system is majoritarian.} Thirteen studies use OLS, 17 use panel
data, 3 use instrumental variable estimation, and 3 employ regression
discontinuity designs. Table \ref{tab:descriptive} shows the descriptive
statistics of the moderator variables.

% Adicionar primeira coluna com estatística descritiva *dos papers* para
% completar as dos coeficientes.

@@

\begin{table}[htpb]
 \caption{Descriptive Statistics of Moderators}
 \centering
 \begin{tabular}{lccc}
    \hline  \hline
    & Main Coefficients & Other Coefficients &   All Coefficients    \\ 
    &        N=36        &       N=92        &    N=128    \\ 
    \hline     
    Independent Variables: &             &                    &                  \\
$\qquad$K &    9 (25.0\%)      &     29 (31.5\%)    & 38 (29.7\%)  \\ 
$\qquad$N &      21 (58.3\%)     &    51 (55.4\%)   & 72 (56.2\%)  \\ 
$\qquad$logN &      6 (16.7\%)     &     12 (13.0\%)    & 18 (14.1\%)  \\ 
Year &     2009 (6.50)    &    2008 (5.75)   & 2008 (5.98) \\ 
Published work: &             &                    &                  \\ 
$\qquad$Yes &     30 (83.3\%)     &    74 (80.4\%)    & 104 (81.2\%) \\ 
$\qquad$No &    6 (16.7\%)       &     18 (19.6\%)   & 24 (18.8\%)  \\ 
Electoral system: &             &                    &                  \\ 
$\qquad$Majoritarian &     18 (50.0\%)      &    40 (43.5\%)   & 58 (45.3\%)  \\ 
$\qquad$Non-Majoritarian &    18 (50.0\%)       &    52 (56.5\%)   & 70 (54.7\%)  \\ 
Estimation method: &             &                    &                  \\ 
$\qquad$OLS &     13 (36.1\%)     &   43 (46.7\%)     & 56 (43.8\%)  \\ 
$\qquad$PANEL &     17 (47.2\%)     &    40 (43.5\%)    & 57 (44.5\%)  \\ 
$\qquad$IV &     3 (8.33\%)      &     3 (3.26\%)    &  6 (4.69\%)  \\ 
$\qquad$RDD &     3 (8.33\%)      &     6 (6.52\%)    &  9 (7.03\%)  \\ 
Sampling Aggregation Level: &             &                    &                  \\ 
$\qquad$Local &     7 (19.4\%)      &     16 (17.4\%)   & 23 (18.0\%)  \\ 
$\qquad$States &    21 (58.3\%)      &    49 (53.3\%)    & 70 (54.7\%)  \\ 
$\qquad$Countries &     8 (22.2\%)      &     7 (29.3\%)   & 35 (27.3\%)  \\ 
\hline  
\end{tabular}
\label{tab:descriptive}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} The values for the variable \textit{Year} indicate the mean and the standard deviation, respectively.}
\end{minipage}    
\end{table}

@@

In this section, we run a series of meta-regressions with 5 covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (fixed effects, instrumental variables,
OLS, or regression discontinuity design).

@@

\begin{table}[htpb]
\footnotesize
\caption{Meta Regression Results}
\label{tab:regressions}
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
%
Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
                               &  &  &  &  & (0.001) & (0.014)\\
%
Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
%
Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
%
Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
%
Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
%
Method: IV & 1.317 & 0.186 &  &  &  & \\
           & (1.807) & (0.802) &  &  &  & \\
%
Method: RDD &  &  &  &-0.285&  & \\
            &  &  &  & (0.062)*** &  & \\
% 
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}

%% CONFERIR TODOS OS RESULTADOS

>>>>

\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, Brazil, \url{huzeyfealptekin@gmail.com}.} \hspace{.5cm} Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \url{danilofreire@gmail.com}, \url{http://danilofreire.github.io}. Corresponding author.} \hspace{.5cm} Umberto Mignozzetti\thanks{Assistant Professor, School of International Relations, Fundação Getulio Vargas, Brazil, \url{umberto.mignozzetti@fgv.br}, \url{http://umbertomig.com}.} \hspace{.5cm} Catarina Roman\thanks{Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil, \url{catarinamroman@gmail.com}.}}

@@

\vspace{.4cm}
\noindent \textbf{Keywords:} distributive politics; law of $1/n$; legislature size; meta-analysis; public spending

@@

\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System

@@

R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & OLS & M\\
R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & OLS & M\\
T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & IV & NM\\
\begin{tabular}[t]{@{}l@{}}T. Bjedov,\\ S. Lapointe \& \\T. Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & OLS & M\\
\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & OLS & M\\
\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}J. Drew \& \\ B. Dollery\end{tabular} & The Price of Democracy? Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}N. Fiorino \& \\ R. Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & IV & NM\\
\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & RDD & NM\\
\begin{tabular}[t]{@{}l@{}}A. Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & RDD & NM\\
\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & OLS & NM\\
\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & OLS & M\\
\begin{tabular}[t]{@{}l@{}}B. Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & OLS & NM\\
\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & IV & M\\
\begin{tabular}[t]{@{}l@{}}B. Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}P. Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government? Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & RDD & NM\\
\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & Panel & M\\
\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & OLS & NM\\
\begin{tabular}[t]{@{}l@{}}C. Schaltegger \& \\ L. Feld\end{tabular} & Do Large Cabinets Favor Large Governments? Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Panel & NM\\
\begin{tabular}[t]{@{}l@{}}E. Stein,\\ E. Talvi \& \\ A. Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub. & 1998 & Multiple (26) & OLS & NM\\ [1ex]

@@

OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation). Country codes follow the ISO 3166-1 alpha-3 international standard.}

@@

We also coded four moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study ($n$,
log($n$), or $k$). The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) electoral system; 4) estimation method.
Since the literature on the ``law of $1/n$'' is notably diverse, we were
restricted to include only the moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

\begin{table}[htpb]
 \caption{Descriptive Statistics of Moderators}
 \centering
 \begin{tabular}{lccc}
\hline  \hline
& Main Coefficients & Other Coefficients &   All Coefficients    \\ 
&        N=36        &       N=92        &    N=128    \\ 
\hline     
Independent Variables: &             &                    &                  \\
$\qquad$ $k$ &    9 (25.0\%)      &     29 (31.5\%)    & 38 (29.7\%)  \\ 
$\qquad$ $n$ &      21 (58.3\%)     &    51 (55.4\%)   & 72 (56.2\%)  \\ 
$\qquad$ log($n$) &      6 (16.7\%)     &     12 (13.0\%)    & 18 (14.1\%)  \\ 
Year &     2009 (6.50)    &    2008 (5.75)   & 2008 (5.98) \\ 
Published work: &             &                    &                  \\ 
$\qquad$Yes &     30 (83.3\%)     &    74 (80.4\%)    & 104 (81.2\%) \\ 
$\qquad$No &    6 (16.7\%)       &     18 (19.6\%)   & 24 (18.8\%)  \\ 
Electoral system: &             &                    &                  \\ 
$\qquad$Majoritarian &     18 (50.0\%)      &    40 (43.5\%)   & 58 (45.3\%)  \\ 
$\qquad$Non-Majoritarian &    18 (50.0\%)       &    52 (56.5\%)   & 70 (54.7\%)  \\ 
Estimation method: &             &                    &                  \\ 
$\qquad$OLS &     13 (36.1\%)     &   43 (46.7\%)     & 56 (43.8\%)  \\ 
$\qquad$Panel &     17 (47.2\%)     &    40 (43.5\%)    & 57 (44.5\%)  \\ 
$\qquad$IV &     3 (8.33\%)      &     3 (3.26\%)    &  6 (4.69\%)  \\ 
$\qquad$RDD &     3 (8.33\%)      &     6 (6.52\%)    &  9 (7.03\%)  \\ 
\hline  
\end{tabular}
\label{tab:descriptive}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} The values for the variable \textit{Year} indicate the mean and the standard deviation, respectively.}
\end{minipage}    
\end{table}

@@

In this section, we run a series of meta-regressions with 5 covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (panel data, instrumental variables,
OLS, or regression discontinuity design).

@@

\begin{table}[htpb]
\footnotesize
\caption{Meta Regression Results}
\label{tab:regressions}
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
                               &  &  &  &  & (0.001) & (0.014)\\
%
Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
%
Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
%
Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
%
Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
%
Method: IV & 1.317 & 0.186 &  &  &  & \\
           & (1.807) & (0.802) &  &  &  & \\
%
Method: RDD &  &  &  &-0.285&  & \\
            &  &  &  & (0.062)*** &  & \\
% 
Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}
